Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-07 WSSSPE3/report/WSSSPE3_review.tex
more tweaks in intro section
Former-commit-id: 9f9e958b75387421aa64ca30005f23e91d8c0ce8

\todo{update this paragraph for WSSSPE3}
The workshop included multiple mechanisms for participation,
encouraged team building around solutions, and identified risky solutions with
potentially transformative outcomes. It strongly encouraged participation of
early-career scientists, postdoctoral researchers, and graduate students, with
funds provided to the conference organizers by the Moore Foundation, the
National Science Foundation (NSF), and the Software Sustainability Institute,
to support the travel of potential
participants who would not otherwise be able to attend and young participants
and those from underrepresented groups. These funds allowed \todo{update}17
additional participants to attend.

@@

\todo{need to update this section for WSSSPE3}
WSSSPE2 began with a call for papers~\cite{WSSSPE2-pre-report}. Based on the
goal of encouraging a wide range of submissions from those involved in software
practice, ranging from initial thoughts and partial studies to mature
deployments, but focusing on papers that are intended to lead to changes, the
organizers wanted to make submission as easy as possible. The call for papers
stated:

>>>>

The workshop included multiple mechanisms for participation and 
encouraged team building around solutions. It strongly encouraged participation of
early-career scientists, postdoctoral researchers, and graduate students, with
funds provided to the conference organizers by the Moore Foundation, the
National Science Foundation (NSF), and the Software Sustainability Institute,
to support the travel of potential
participants who would not otherwise be able to attend, younger participants
and those from underrepresented groups. These funds allowed 16
additional participants to attend.

@@

\todo{need to update this section for WSSSPE3}
WSSSPE2 began with a call for papers. Based on the
goal of encouraging a wide range of submissions from those involved in software
practice, ranging from initial thoughts and partial studies to mature
deployments, but focusing on papers that are intended to lead to changes, the
organizers wanted to make submission as easy as possible. The call for papers
stated:
